Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-09-08 doc/manuscript/ESSDmanuscript.Rmd
mention new CI system

## Quality control measures
Prior to releasing ForC v4.0, we executed several quality control measures.
First, to improve information on geographic coordinates, we flagged and reviewed records with suspected low precision *(Issue #29)[https://github.com/forc-db/ForC/issues/229]*.
Second, to identify erroneous climate data... *(Issue #212)[https://github.com/forc-db/ForC/issues/212]*.

>>>>

## Quality control measures
Prior to releasing ForC v4.0, we executed several quality control measures.
First, we implemented a system of continuous integration using GitHub Actions (*sensu* Kim et al. in prep) to run some automatic checks any time the master data files are updated.
Second, to improve information on geographic coordinates, we flagged and reviewed records with suspected low precision *(Issue #29)[https://github.com/forc-db/ForC/issues/229]*.
Third, to identify erroneous climate data... *(Issue #212)[https://github.com/forc-db/ForC/issues/212]*.

### 2021-09-08 doc/manuscript/ESSDmanuscript.tex
mention new CI system

Prior to releasing ForC v4.0, we executed several quality control
measures. First, to improve information on geographic coordinates, we
flagged and reviewed records with suspected low precision \emph{(Issue
\#29){[}https://github.com/forc-db/ForC/issues/229{]}}. Second, to
identify erroneous climate data\ldots{} \emph{(Issue
\#212){[}https://github.com/forc-db/ForC/issues/212{]}}.

>>>>

Prior to releasing ForC v4.0, we executed several quality control
measures. First, we implemented a system of continuous integration using
GitHub Actions (\emph{sensu} Kim et al.~in prep) to run some automatic
checks any time the master data files are updated. Second, to improve
information on geographic coordinates, we flagged and reviewed records
with suspected low precision \emph{(Issue
\#29){[}https://github.com/forc-db/ForC/issues/229{]}}. Third, to
identify erroneous climate data\ldots{} \emph{(Issue
\#212){[}https://github.com/forc-db/ForC/issues/212{]}}.
